ext_risk_copula

### 2019-01-22 ext_risk_copula.Rmd
adding Pennycuick model results

```{r fig_msmith_r_vary_localdisp, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 1.7) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/msmith/msmith_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 1.7) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/msmith/msmith_ext_risk_global_disp.pdf){ width=40%, height=40% }

@@

>>>>

```{r fig_msmith, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 4/3) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/msmith/msmith_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 4/3) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/msmith/msmith_ext_risk_global_disp.pdf){ width=40%, height=40% }

@@

# Pennycuick model :

```{r get_rc_pennycuick,echo=F,cache=T,cache.extra=list(seed,mtime("1var_pop_model_bifurcation.R"))}
source("./1var_pop_model_bifurcation.R")
a_pennycuick<-0.1
b_pennycuick<-0.1
eps<-1e-10 #you can change it upto which decimal point you want it to be exact
rlist<-seq(from=4.3231657,to=4.3231658,by=eps)
res_pennycuick<-c() 
for(r in rlist){
  ans<-fn_d1_eqm(params=c(r,a,b),model="pennycuick")
  res_pennycuick<-c(res_pennycuick,ans)
}

#plot(rlist,res_pennycuick,col="red",type="l",xlab="r",ylab="pennycuick_1st_der_at_eqm")
#abline(h=0)

rc_pennycuick<-rlist[which.min(abs(res_pennycuick-0))]
formatC(rc_pennycuick,digits = 10, format="f") # accurate upto 10th decimal
```

```{r fig_pennycuick, echo=F,  results="hide", cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
model<-"pennycuick"

numsims<-10000
numsteps<-25
numlocs<-5
a<-a_pennycuick
b<-b_pennycuick
scl<-1

rlist<-sort(c(seq(from=2,to=7,by=0.5),rc_pennycuick))

pennycuick_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist))) # a dataframe to store ext risk at dispersal d=0 for all r
colnames(pennycuick_extrisk_d0)<-c("r","risk_left_d0","risk_right_d0")

# plot for local dispersal in D matrix 
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    K_e<-(b/a)*(a+log(r-1))
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    pennycuick_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    pennycuick_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

saveRDS(pennycuick_extrisk_d0,paste(resloc,"pennycuick_extrisk_d0.RDS",sep=""))

# plot for global dispersal in D matrix 
pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    K_e<-(b/a)*(a+log(r-1))
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/pennycuick/pennycuick_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 1, b = 3) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/pennycuick/pennycuick_ext_risk_global_disp.pdf){ width=40%, height=40% }
